EGGs are adhesive!

### 2025-05-06 calco/final.tex
minori

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\E{\textbf {\textup{E}}}
\def\T{\textbf {\textup{1}}}
\def\A{\textbf {\textup{A}}}
\def\M{\mathcal{M}}
%categorie varie
\newcommand{\catname}[1]{\textbf{\textup{#1}}}
\newcommand{\lab}{\catname{LHyp}}
\newcommand{\hyp}{\catname{Hyp}}
\newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
\newcommand{\EqHyp}{\catname{EqHyp}} %equivalence hypergraphs
\newcommand{\EqHyps}{\catname{EqHyp}_{\Sigma}}
\newcommand{\EqTG}{\catname{EqTG}}
\newcommand{\EqTGs}{\catname{EqTG}_{\Sigma}}
\newcommand{\GEqTGs}{\catname{GEqTG}_{\Sigma}}
\newcommand{\GEqATGs}{\catname{GEqATG}_{\Sigma}}
\newcommand{\gr}{\textbf{\textup{Graph}}}
\newcommand{\dgr}{\catname{SGraph}}
\newcommand{\dg}{\catname{DAG}}
\newcommand{\rt}{\mathsf{dcl_s}}
\newcommand{\rta}{\mathsf{dcl}}
\newcommand{\rtd}{\mathsf{dcl_{d}}}
\newcommand{\slice}[2]{(\catname{#1}\downarrow{#2})}
\newcommand{\tg}[0]{\catname{TG}_{\Sigma}}
\newcommand{\teg}[0]{\catname{TeGr}_{\Sigma}}
\newcommand{\sv}[0]{\mathsf{Sieves}}
\newcommand{\mono}[1]{\mathsf{Mon}(\catname{#1})}
\newcommand{\mo}[1]{{#1}_\mathsf{Mon}}
\newcommand{\pro}{\mathsf{prod}}
\newcommand{\spro}{\mathsf{ps}}
\newcommand{\prol}{\mathsf{lprod}}
\newcommand{\pred}[1]{{\downarrow}#1}
\newcommand{\colim}[0]{\mathrm{colim}}
\newcommand{\cod}{\mathsf{cod}}
\renewcommand{\sp}{\mathsf{sp}}
\renewcommand{\sup}{\mathsf{sup}}
\newcommand{\cow}[1]{\mathsf{cwd}({#1})}
\renewcommand{\inf}{\mathsf{inf}}
\newcommand{\dom}{\mathsf{dom}}
\newcommand{\dwnarrow}{\downarrow \hspace{-2pt}}
\newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
\newcommand{\egg}{\catname{GEqHyp}}

@@

\begin{definition}\label[definition]{def:tg}\index{term graph}
	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is a mono. We define $\tg$ to be the full subcategory of $\hyp_{\Sigma}$ and denote by $I_\Sigma$ the inclusion. Restricting $U_\Sigma\colon \hyp_{\Sigma}\to \catname{Set}$ we get a forgetful functor $U_{\tg}\colon \tg\to \catname{Set}$.
\end{definition}

@@

We now examine some properties of $\tg$, in order to study its adhesivity properties.

@@

\begin{lemma}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$. Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout along $(f_2, g_2)$,  then their pushout $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ is a term graph too.
\end{lemma}

\Cref{thm:slice-functors}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05}.
\begin{corollary}\label{cor:term}
	The category $\tg$ is quasiadhesive.
\end{corollary}

@@

\begin{definition}
	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, Q_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $Q_\mathcal{G}$ is a set and $q_{\mathcal{G}}: V_{\mathcal{G}}\eto Q_{\mathcal{G}}$ is a surjection called \emph{quotient map}. 
	%
	A morphism $h\colon \mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute
	\[\xymatrix@R=15pt{
		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_C} \\
		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar@{>>}[r]_{q_\mathcal{H}} & {Q_\mathcal{H}}
	}\]
	The category of hypergraphs with equivalence and their morphisms is denoted $\EqHyp$.

@@

Combining together the previous corollary with \Cref{rem:eqhyp_morphs} we get the following characterization of monos in $\EqHyp$.

\begin{corollary}\label{cor:mono1}
	An arrow $(h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
\end{corollary}

@@

\noindent
\parbox{11.4cm}{
\begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
Let $F\colon \D \to \EqHyp$ be a diagram and $(E_d, V_d, Q_d, s_d, t_d, q_d)$ the image of an object $d$. Then it holds
\begin{enumerate}
		\item $F$ has a colimit which is preserved by $K$;
	\item if $(L, \{l_d\}_{d\in \D})$ is a limiting cocone for $K \circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$, where $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ is limiting for $T\circ F$.
\end{enumerate}
\end{restatable}}\hfill 
\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}

@@

\commentato{
\begin{remark}
	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
	in fact $q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E = q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G} = h_C^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}$.
	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
\end{remark}
}

@@

\noindent
\parbox{10cm}{
\begin{definition}
	We define $\pbc$ as the class of  regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
\end{definition}
} \hfill
	\parbox{2cm}{
	     \xymatrix@R=18pt{
	        V_\mathcal{G} \ar@{>>}[d]_{q_\mathcal{G}} \ar@{>->}[r]_{h_V}& V_\mathcal{H} \ar@{>>}[d]^{q_\mathcal{H}} \\
	        Q_\mathcal{G} \ar@{>->}[r]^{h_Q} & Q_\mathcal{{H}}
              }
         }

@@

Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$. From the second point of \Cref{thm:slice-functors,prop:eqhyp_complete,lim} we can deduce the following.

@@

\noindent
\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $J_\Sigma$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.  Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill 
\parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]_{h_Q}& Q_{\mathcal{H}}} }

@@

A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proof are in \Cref{proof:elim}.

@@

\begin{corollary}\label{cor:ereg}
	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\hyp$. 
\end{corollary}

@@

\noindent
\parbox{11.4cm}{
\comp*}\hfill 
\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>->}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}

@@

	\noindent 
\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside. Notice moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$. By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback. By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}

>>>>

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\E{\textbf {\textup{E}}}
\def\T{\textbf {\textup{1}}}
\def\A{\textbf {\textup{A}}}
\def\M{\mathcal{M}}
%categorie varie
\newcommand{\catname}[1]{\textbf{\textup{#1}}}
\newcommand{\lab}{\catname{LHyp}}
\newcommand{\hyp}{\catname{Hyp}}
\newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
\newcommand{\EqHyp}{\catname{EqHyp}} %equivalence hypergraphs
\newcommand{\EqHyps}{\catname{EqHyp}_{\Sigma}}
\newcommand{\EqTG}{\catname{EqTG}}
\newcommand{\EqTGs}{\catname{EqTG}_{\Sigma}}
\newcommand{\GEqTGs}{\catname{GEqTG}_{\Sigma}}
\newcommand{\GEqATGs}{\catname{GEqATG}_{\Sigma}}
\newcommand{\gr}{\textbf{\textup{Graph}}}
\newcommand{\dgr}{\catname{SGraph}}
\newcommand{\dg}{\catname{DAG}}
\newcommand{\rt}{\mathsf{dcl_s}}
\newcommand{\rta}{\mathsf{dcl}}
\newcommand{\rtd}{\mathsf{dcl_{d}}}
\newcommand{\slice}[2]{(\catname{#1}\downarrow{#2})}
\newcommand{\tg}[0]{\catname{TG}_{\Sigma}}
\newcommand{\teg}[0]{\catname{TeGr}_{\Sigma}}
\newcommand{\sv}[0]{\mathsf{Sieves}}
\newcommand{\mono}[1]{\mathsf{Mon}(\catname{#1})}
\newcommand{\mo}[1]{{#1}_\mathsf{Mon}}
\newcommand{\pro}{\mathsf{prod}}
\newcommand{\spro}{\mathsf{ps}}
\newcommand{\prol}{\mathsf{lprod}}
\newcommand{\pred}[1]{{\downarrow}#1}
\newcommand{\colim}[0]{\mathrm{colim}}
\newcommand{\cod}{\mathsf{cod}}
\renewcommand{\sp}{\mathsf{sp}}
\renewcommand{\sup}{\mathsf{sup}}
\newcommand{\cow}[1]{\mathsf{cwd}({#1})}
\renewcommand{\inf}{\mathsf{inf}}
\newcommand{\dom}{\mathsf{dom}}
\newcommand{\dwnarrow}{\downarrow \hspace{-2pt}}
\newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
\newcommand{\egg}{\mathsf{e}\text{-}\catname{EqHyp}}

@@

\begin{definition}\label[definition]{def:tg}\index{term graph}
	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is a mono. We define $\tg$ to be the full subcategory of $\hyp_{\Sigma}$ given by term graphs and denote by $I_\Sigma$ the inclusion. Restricting $U_\Sigma\colon \hyp_{\Sigma}\to \catname{Set}$ we get a forgetful functor $U_{\tg}\colon \tg\to \catname{Set}$.
\end{definition}

@@

\begin{example}
The labelled hypergraph of \Cref{lab_2} is a term graph.
\end{example}

We now examine some properties of $\tg$, in order to study its adhesivity properties. We begin noticing that, for every set $X$,  $\Delta_\Sigma(X)$ has no hyperedges and so is a term graph. this yields at once the following.

@@

\begin{lemma}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$. Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout  $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ along $(f_2, g_2)$ is a term graph too.
\end{lemma}

\Cref{thm:slice-functors,prop:mono}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05} (see also \cite[Cor.~5.15]{CastelnovoGM24} for the details of the argument presented here).
\begin{corollary}\label{cor:term}
	The category $\tg$ is quasiadhesive.
\end{corollary}

@@

\begin{definition}
	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, Q_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $Q_\mathcal{G}$ is a set and $q_{\mathcal{G}}: V_{\mathcal{G}}\eto Q_{\mathcal{G}}$ is a surjection called \emph{quotient map}. 
	%
	A morphism $h\colon \mathcal{G\to H}$ is a triple $(h_E, h_V, h_Q)$ such that the following diagrams commute
	\[\xymatrix@R=15pt{
		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_Q} \\
		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar@{>>}[r]_{q_\mathcal{H}} & {Q_\mathcal{H}}
	}\]
	The category of hypergraphs with equivalence and their morphisms is denoted $\EqHyp$.

@@

From the previous results we get the following characterization of monos in $\EqHyp$.

\begin{corollary}\label{cor:mono1}
	An arrow $(h_E, h_V, h_Q): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
\end{corollary}

@@

\noindent
\parbox{11.4cm}{
\begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
Let $F\colon \D \to \EqHyp$ be a diagram and $(E_d, V_d, Q_d, s_d, t_d, q_d)$ the image of an object $d$. Then it holds
\begin{enumerate}
		\item $F$ has a colimit which is preserved by $K$;
	\item consider a cone $(L, \{l_d\}_{d\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$.
\end{enumerate}
\end{restatable}}\hfill 
\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}

@@

\commentato{
\begin{remark}
	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
	in fact $q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E = q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G} = h_Q^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}$.
	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
\end{remark}
}

@@

\noindent
\parbox{11cm}{
\begin{definition}
	We define $\pbc$ as the class of  regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
\end{definition}
} \hfill
	\parbox{2cm}{
	     \xymatrix@R=18pt{
	        V_\mathcal{G} \ar@{>>}[r]_{q_\mathcal{G}} \ar@{>->}[d]_{h_V}& Q_\mathcal{G} \ar@{>->}[d]^{h_Q}\\
	        V_\mathcal{H} \ar@{>>}[r]^{q_\mathcal{H}}  & Q_\mathcal{{H}}
              }
         }

@@

Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$. From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.

@@

\noindent
\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $J_\Sigma$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.  By \Cref{lem:reg,prop:monos_in_eqhyps}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill 
\parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]_{h_Q}& Q_{\mathcal{H}}} }

@@

\begin{example}
	Consider the hypergraph of $\mathcal{G}$ \Cref{exa_2} and consider as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$. Then the kernel pair of $\id{V^\star_\mathcal{G}} \circ s$ concide with the kernel pair of $s$ which is empty. Thus  $\mathcal{G}$ is, trivially, an e-hypergraph
\end{example}
A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proof are in \Cref{proof:elim}.

@@

\begin{corollary}\label{cor:ereg}
	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is a regular mono in $\hyp$. 
\end{corollary}

@@

\noindent
\parbox{11.4cm}{
\comp*}\hfill 
\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}

@@

	\noindent 
\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside. Notice moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$. By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback. By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_Q} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
